---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# fontscales

<!-- badges: start -->
<!-- badges: end -->

The goal of fontscales is to is to let you use fancy iconographic fonts with ease in [ggplot2](https://ggplot2.tidyverse.org/).

## Installation

You can install the dev version of fontscales from [Github](http://github.com/) with:

```{r installation, eval=FALSE}
require("devtools")
install_github("tidymodels/fontscales")
```

## StateFace

The [StateFace](https://propublica.github.io/stateface/) font by [ProPublica](https://www.propublica.org/) contains the 50 different U.S. states as tiny glyphs and can thus be used in data visualizations.

The data set `usa_arrests` represents a data set where this might be useful where the `state` variable contains the name of the state

```{r}
library(fontscales)
usa_arrests
```

Using `ggplot2` you pass the state name variable to the `label` aesthetic and use `geom_stateface()` to draw the states. (This should function similary to `geom_text()` or `geom_point()`).

```{r}
library(ggplot2)
ggplot(usa_arrests, aes(murder, assault, label = state, color = urban_pop)) +
  geom_stateface()
```

And other `ggplot2` functions work as expected

```{r}
library(tidyr)
usa_arrests %>%
  pivot_longer(-c(state, urban_pop)) %>%
  ggplot(aes(urban_pop, value, label = state)) +
  geom_stateface() +
  facet_wrap(~name, scales = "free_y")
```

